---
title: "Lab 6 Comparing two means"
author: ""
date: "`r Sys.Date()`"
output: github_document
---

Researchers studying the number of electric fish species living in various parts of the Amazon basin were interested in whether the presence of tributaries affected the local number of electric fish species in the main rivers (Fernandes et al. 2004).

They counted the number of electric fish species above and below the entrance point of a major tributary at 12 different river locations.

The data is provided in your GitHub repository.

For each question below, write a sentence answering the question and show the code you used to come up with the answer, if applicable.

## Question A

> Test the hypothesis that the tributaries have no effect on the number of species of electric fish.

```{r t-test}
library(tidyverse)
library(ggplot2)

fish <- read_csv("chap12q19ElectricFish.csv")

fish_long <- 
  pivot_longer(fish, speciesUpstream:speciesDownstream,
               names_to = "location",
               values_to = "species") %>% 
  mutate(location = str_remove(location, c("species"))) %>% 
  print()

fish_ttest <- t.test(species ~ location, data = fish_long)
fish_ttest$estimate
```

ANSWER: Mean downstream: 16.41667
Mean upstream: 14.58333

## Question B

> What is the difference in the mean numbers of species between areas upstream and downstream of a tributary? What is the 95% confidence interval of this difference in means?

ANSWER: Very basically there are more species of fish downstream than there are upstream. 
Difference in mean: 1.83334
95% confidence intervals: -4.587031 and 8.253697

## Question C

> State the assumptions that you had to make to complete parts (A) and (B). Create a graph to assess whether one of those assumptions was met.

ANSWER: Units are randomly sampled and the paired differences have a normal distribution in populations. Both assumptions appear to be not met. 

```{r}
distinct(fish_long, tributary, species, location)

ggplot(data = fish_long, 
       mapping = aes(x = tributary, 
           y = species, 
           fill = location)) + 
  geom_bar(stat = "identity",
           position = "dodge")
```
